Variational Monte Carlo on bosonic systems

### 2018-01-22 project_1/article/article.tex
Add description of the full problem
Add solution to the first derivative

>>>>

        \subsubsection{The full system}
            Moving to the full system allowing $\beta$ to vary and setting $a
            \neq 0$ we write the trial wavefunction as
            \begin{align}
                \bra{\vf{r}}\ket{\Psi_T}
                &= \prod_i^N \phi(\vf{r}_i)
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr),
            \end{align}
            where $r_{ij} = |\vf{r}_i - \vf{r}_j|$ and
            \begin{align}
                u(r_{ij}) = \ln\bigl[f(a, \vf{r}_i, \vf{r}_j)\bigr],
            \end{align}
            we wish to compute the local energy. The gradient is thus given by
            \begin{align}
                \bra{\vf{r}}\nabla_k\ket{\Psi_T}
                &= \nabla_k\brac{
                    \prod_i^N\phi(\vf{r}_i)
                    \exp\Biggl(
                        \sum_{i < j}^N u(r_{ij})
                    \Biggr)
                } \\
                &=
                \Biggl\{
                    \nabla_k
                    \prod_i^N\phi(\vf{r}_i)
                \Biggr\}
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &\qquad
                +
                \prod_i^N\phi(\vf{r}_i)
                \nabla_k
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &=
                \nabla_k\phi(\vf{r}_k)
                \prod_{i \neq k}^N \phi(\vf{r}_i)
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &\qquad
                +
                \prod_i^N\phi(\vf{r}_i)
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &\qquad
                \times
                \nabla_k
                \Biggl(
                    \sum_{i < l}^N u(r_{il})
                \Biggr).
            \end{align}
            The last term is extracted from the chain rule and can be evaluated
            as
            \begin{align}
                \nabla_k
                \Biggl(
                    \sum_{i < l}^N u(r_{il})
                \Biggr)
                &= \begin{cases}
                    \nabla_k u(r_{ik}) & i < k, \\
                    \sum_{k < l}^N \nabla_k u(r_{kl}) & i = k.
                \end{cases}
            \end{align}
            As $r_{ij} = r_{ji}$ we can rewrite the first case to
            \begin{align}
                \nabla_k u(r_{ik}) = \nabla_k u(r_{ki}).
            \end{align}
            Here $i$ varies with the product thus we get
            \begin{align}
                \nabla_k
                \Biggl(
                    \sum_{i < l}^N u(r_{il})
                \Biggr)
                &=
                \sum_{l \neq k}^N\nabla_k u(r_{kl}).
            \end{align}
            We are thus left with
            \begin{align}
                \bra{\vf{r}}\nabla_k\ket{\Psi_T}
                &=
                \nabla_k\phi(\vf{r}_k)
                \prod_{i \neq k}^N \phi(\vf{r}_i)
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &\qquad
                +
                \prod_i^N\phi(\vf{r}_i)
                \exp\Biggl(
                    \sum_{i < j}^N u(r_{ij})
                \Biggr) \\
                &\qquad
                \times
                \sum_{l \neq k}^N\nabla_k u(r_{kl}).
            \end{align}
